Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-07-30 Report/dual_approach.tex
updated with Nams' comment (included Manosha's comments as well) Need to update Response

The \ac{ADMM} approach can also be used to decouple the precoder design across multiple \acp{BS} to solve the convex problem in \eqref{eqn-decent-1}. Generally, the \ac{ADMM} is preferred over the \ac{DD} approach in \cite{tolli2011decentralized} for its robustness and improved convergence behavior \cite{boyd2011distributed}. In contrast to the \acl{PD}, the \ac{ADMM} relaxes the interference constraints by including in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}. Similar approach for the precoder design in the minimum power context was considered in \cite{admm_robust}.

Using the formulation presented in \cite{boyd2011distributed,admm_robust}, we can write the \ac{BS} \me{b} specific \ac{ADMM} subproblem for the \me{\ith{i}} iteration as
\iftoggle{single_column}{\allowdisplaybreaks
\begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}\allowdisplaybreaks \neqsub
\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} &\quad& \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(i)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right \|^2 \eqsub \eqspace \\
\text{subject to} &\quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
&\quad&\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n} \eqspace \eqsub \\
&\quad& \sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b} \; \forall \bar{k} \in \bar{\mc{U}}_b \; \forall n \eqsub \\
&\quad& \text{and } \eqsub \eqref{eqn-8}
\end{IEEEeqnarray}
}{\begin{IEEEeqnarray}{rl} \label{eqn-dual-3}\allowdisplaybreaks \neqsub
&\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} \: \; \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(i)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(i)}_b \right \|^2 \eqsub \eqspace \\
&\text{subject to} \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
&\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n} \eqspace \eqsub \\
&\sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b} \; \forall \bar{k} \in \bar{\mc{U}}_b \; \forall n \eqsub \\
& \text{and } \eqsub \eqref{eqn-8}
\end{IEEEeqnarray}}
where \me{\mbfa{\zeta}^{(i)}_b} denotes the interference vector updated from the earlier iteration and \me{\mbfa{\nu}^{(i)}_b} represents the dual vector corresponding to the equality constraint at the \me{\ith{i}} iteration as
\begin{equation} \label{const-admm1}
\mbfa{\zeta}_b = \mbfa{\zeta}^{(i)}_b.
\end{equation}

Upon solving \eqref{eqn-dual-3} for \me{\mbfa{\zeta}_b \forall b} in the \me{\ith{i}} iteration, the next iterate is updated by exchanging the corresponding interference terms between two \acp{BS} \me{b} and \me{b_k} as
\begin{equation}
\mbfa{\zeta}_{b_k}(b)^{(i+1)} = \mbfa{\zeta}_{b}(b_k)^{(i+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}.
\label{if-sg-update}
\end{equation}
The dual vector for the next iteration is updated by using the subgradient search to maximize the dual objective as
\begin{equation}
\mbfa{\nu}_b^{(i+1)} = \mbfa{\nu}_b^{(i)} + \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(i+1)} \right )
\label{dual-sg-update}
\end{equation}
where step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed} to depend on the system model under consideration. The convergence rate of the distributed algorithm is susceptible to the choice of step size parameter \me{\rho}. In numerical simulations, we consider step size \me{\rho=2}. The above iterative procedure is performed until convergence or terminated when exceeding a predetermined number of iterations, say, \eqn{J_{\max}}. The \ac{ADMM} based precoder design is outlined in Algorithm \ref{algo-3}.
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l}}
	\KwInit{\me{i=0,j=0} and \me{{\mbf{m}}_{l,k,n}} satisfying \eqref{power_update}}
	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
	initialize the interference vectors \me{\mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in\mc{B}} \;
	initialize the dual vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
		\Repeat{convergence or \me{i \geq I_{\max}}}{
			\Repeat{convergence or \me{j \geq J_{\max}}}{
				solve for \me{\mvec{m}{l,k,n}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
				update \me{\mbfa{\zeta}^{(j+1)}_b} and \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{if-sg-update} and \eqref{dual-sg-update}\;
				update \me{j = j + 1}\;
			}
			send precoded downlink pilot with \me{\mbf{m}}\;
			evaluate \me{\mvec{w}{l,k,n}} at each user and inform to all \acp{BS} in \eqn{\mc{B}} using uplink precoded pilots \cite{komulainen2013effective} \;
			update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
			$i = i + 1$, \me{j=0} \;
		}
	}
	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
	\label{algo-3}
\end{algorithm}

The convergence analysis for the distributed algorithms is provided in Appendix \ref{sec-dist-conv}. \review{In practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few number of steps, say, \eqn{J_{\max}}. If so, the convergence of the iterates is not guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step. It follows from the fact that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically, despite reaching the centralized solution upon convergence. However, if the distributed algorithms are performed for adequate number of iterations to ensure strict monotonicity of the objective in each \ac{SCA} step, then the limit point of the sequence of iterates is a stationary point of \eqref{eqn-6}.}

@@

\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right ) + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
\text{subject to} && \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,k,n} |^2 + \sum_{{\hat{b}} \in \bar{\mc{B}}_{b}} \zeta^{\set{b}(i-1)}_{l,k,n,{\hat{b}}} \nonumber \\

@@

&& \zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2 \; \forall \pr{k} \in \bar{\mc{U}}_{b}, \; \forall n \in \mc{N} \IEEEyessubnumber \label{eqn-dual-1e} \\

@@

\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} && \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right )  \nonumber \\
&& + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a}  \\

@@

\beta_{l,k,n} \geq \sum_{\mathclap{j = 1,j \neq l}}^L && |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,k,n} |^2 + \sum_{{\hat{b}} \in \bar{\mc{B}}_{b}} \zeta^{\set{b}(i-1)}_{l,k,n,{\hat{b}}} \nonumber \\

@@

\zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} && \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2, \forall \pr{k} \in \bar{\mc{U}}_{b} \IEEEyessubnumber \eqspace \label{eqn-dual-1e} \\

@@

where the superscript \me{i} represents the current iteration or the information exchange index and \me{\mbfa{\zeta}^{(i-1)}} denotes the updated global interference level from the \me{\ith{(i-1)}} information exchange of the local interference vector \me{\mbfa{\zeta}^{\set{b}(i-1)}, \forall b \in \mc{B}}.

>>>>

The \ac{ADMM} approach can also be used to decouple the precoder design across multiple \acp{BS} to solve the convex subproblem in \eqref{eqn-decent-1}. Generally, the \ac{ADMM} is preferred over the \acl{DD} in \cite{tolli2011decentralized} for its robustness and improved convergence behavior \cite{boyd2011distributed}. In contrast to the \acl{PD}, the \ac{ADMM} relaxes the interference constraints by including in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}. Similar approach for the precoder design in the minimum power context was considered in \cite{admm_robust}.

Using the formulation presented in \cite{boyd2011distributed,admm_robust}, we can write the \ac{BS} \me{b} specific \ac{ADMM} subproblem for the \me{\ith{j}} iteration as
\iftoggle{single_column}{\allowdisplaybreaks
\begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}\allowdisplaybreaks \neqsub
\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} &\quad& \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(j)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b \right \|^2 \eqsub \eqspace \\
\text{subject to} &\quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
&\quad&\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n} \eqspace \eqsub \\
&\quad& \sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b} \; \forall \bar{k} \in \bar{\mc{U}}_b \; \forall n \eqsub \\
&\quad& \text{and } \eqsub \eqref{eqn-8}
\end{IEEEeqnarray}
}{\begin{IEEEeqnarray}{rl} \label{eqn-dual-3}\allowdisplaybreaks \neqsub
&\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}_b}}{\text{minimize}} \: \; \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{(j)\,\tran}_b  \left ( \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b \right ) +  \frac{\rho}{2} \left \| \mbfa{\zeta}_b - \mbfa{\zeta}^{(j)}_b \right \|^2 \eqsub \eqspace \\
&\text{subject to} \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \eqsub \label{power_update} \\
&\sum_{\bar{b} \in \bar{\mc{B}}_b} \zeta_{l,k,n,\bar{b}} + \sum_{\mathclap{\{\bar{l},\bar{k}\}\neq\{l,k\}}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{\bar{l},\bar{k},n} |^2 + \enoise \leq \beta_{l,k,n} \eqspace \eqsub \\
&\sum_{k \in \mc{U}_b} \sum_{l=1}^L |\mvec{w}{\bar{l},\bar{k},n}^\herm \mvec{H}{b,\bar{k},n} \mvec{m}{l,k,n} |^2 \leq \zeta_{\bar{l},\bar{k},n,b} \; \forall \bar{k} \in \bar{\mc{U}}_b \; \forall n \eqsub \\
& \text{and } \eqsub \eqref{eqn-8}
\end{IEEEeqnarray}}
where \me{\mbfa{\zeta}^{(j)}_b} denotes the interference vector updated from the earlier iteration and \me{\mbfa{\nu}^{(j)}_b} represents the dual vector corresponding to the equality constraint at the \me{\ith{j}} iteration as
\begin{equation} \label{const-admm1}
\mbfa{\zeta}_b = \mbfa{\zeta}^{(j)}_b.
\end{equation}

Upon solving \eqref{eqn-dual-3} for \me{\mbfa{\zeta}_b \forall b} in the \me{\ith{j}} iteration, the next iterate is updated by exchanging the corresponding interference terms between two \acp{BS} \me{b} and \me{b_k} as
\begin{equation}
\mbfa{\zeta}_{b_k}(b)^{(j+1)} = \mbfa{\zeta}_{b}(b_k)^{(j+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}.
\label{if-sg-update}
\end{equation}
The dual vector for the next iteration is updated by using the subgradient search to maximize the dual objective as
\begin{equation}
\mbfa{\nu}_b^{(j+1)} = \mbfa{\nu}_b^{(j)} + \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(j+1)} \right )
\label{dual-sg-update}
\end{equation}
where step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed} to depend on the system model under consideration. The convergence rate of the distributed algorithm is susceptible to the choice of step size parameter \me{\rho}. In numerical simulations, we consider step size \me{\rho=2}. The above iterative procedure is performed until convergence or terminated when exceeding a predetermined number of iterations, say, \eqn{J_{\max}}. The \ac{ADMM} based precoder design is outlined in Algorithm \ref{algo-3}.
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall users}}
	\KwInit{\me{i=0,j=0} and \me{{\mbf{m}}_{l,k,n}} satisfying \eqref{power_update}}
	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
	initialize the vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
		\Repeat{convergence or \me{i \geq I_{\max}}}{
			\Repeat{convergence or \me{j \geq J_{\max}}, \me{\forall b \in \mc{B}}}{
				solve for \me{\mvec{m}{l,k,n}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
				update \me{\mbfa{\zeta}^{(j+1)}_b} and \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{if-sg-update} and \eqref{dual-sg-update}\;
				update \me{j = j + 1}\;
			}
			send precoded downlink pilot with \me{\mbf{m}}\;
			evaluate \me{\mvec{w}{l,k,n}} at each user and inform to all \acp{BS} in \eqn{\mc{B}} using uplink precoded pilots \cite{komulainen2013effective} \;
			update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
			$i = i + 1$, \me{j=0} \;
		}
	}
	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
	\label{algo-3}
\end{algorithm}
%\begin{algorithm}
%	\SetAlgoLined
%	\DontPrintSemicolon
%	\BlankLine
%	\SetKwInput{KwInit}{Initialize}
%	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
%	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall users}}
%	\KwInit{\me{i=0,j=0} and \me{{\mbf{m}}_{l,k,n}} satisfying \eqref{power_update}}
%	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
%	initialize the vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
%	\Repeat{convergence or \me{i \geq I_{\max}}}{ 
%		\Repeat{convergence or \me{k \geq K_{\max}}}{
%			\Repeat{convergence or \me{j \geq J_{\max}}, \me{\forall b \in \mc{B}}}{
%				solve for \me{\{\mbf{m}\}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
%				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
%				update \me{\mbfa{\zeta}^{(j+1)}_b} and \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{if-sg-update} and \eqref{dual-sg-update}\;
%				update \me{j = j + 1}\;
%			}
%			update \me{\{\tilde{\mbf{u}}\}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\{\tilde{\epsilon}\}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
%			$k = k + 1$, \me{j=0} \;
%		}
%		using \me{\{\mbf{m}\}}, update the receivers \me{\{\mbf{w}\}} of all users \;		
%		update \me{\{\tilde{\mbf{u}}\}} or \me{\{\tilde{\epsilon}\}} respectively with \me{\{\mbf{m}\}} and \me{\{\mbf{w}\}} \;
%		$i = i + i$, \me{k=0} \;
%	}
%	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
%	\label{algo-3}
%\end{algorithm}

The convergence analysis for the distributed algorithms is provided in Appendix \ref{sec-dist-conv}. \review{To reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few steps, say, \eqn{J_{\max}}. If so, the convergence of the iterates is not guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step. The reason is that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically, despite reaching the centralized solution upon convergence. However, if the distributed methods are performed for an adequate number of iterations to ensure the strict monotonicity of the objective sequence in each \ac{SCA} update, then the limit point of the sequence of iterates is a stationary point of the nonconvex problem \eqref{eqn-6}.} %Note that the receivers can also be updated together with the transmit precoders in each \ac{SCA} step, \textit{i.e.}, \eqn{K_{\max} = 1}, since the \ac{MMSE} receivers are optimal for fixed transmit precoders obtained in each \ac{SCA} step.}

@@

\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(j)}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(j-1)}T} \left ( \mbfa{\zeta}^{\set{b}(j)} - \mbfa{\zeta}^{(j-1)}(b) \right ) + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(j)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(j-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
\text{subject to} && \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,k,n} |^2 + \sum_{{\hat{b}} \in \bar{\mc{B}}_{b}} \zeta^{\set{b}(j-1)}_{l,k,n,{\hat{b}}} \nonumber \\

@@

&& \zeta^{\set{b}(j)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2 \; \forall \pr{k} \in \bar{\mc{U}}_{b}, \; \forall n \in \mc{N} \IEEEyessubnumber \label{eqn-dual-1e} \\

@@

\underset{\substack{\gamma_{l,k,n}, \mvec{m}{l,k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(j)}}}{\text{minimize}} && \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(j-1)}T} \left ( \mbfa{\zeta}^{\set{b}(j)} - \mbfa{\zeta}^{(j-1)}(b) \right )  \nonumber \\
&& + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(j)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(j-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a}  \\

@@

\beta_{l,k,n} \geq \sum_{\mathclap{j = 1,j \neq l}}^L && |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,k,n} |^2 + \sum_{{\hat{b}} \in \bar{\mc{B}}_{b}} \zeta^{\set{b}(j-1)}_{l,k,n,{\hat{b}}} \nonumber \\

@@

\zeta^{\set{b}(j)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} && \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2, \forall \pr{k} \in \bar{\mc{U}}_{b} \IEEEyessubnumber \eqspace \label{eqn-dual-1e} \\

@@

where the superscript \me{i} represents the current iteration or the information exchange index and \me{\mbfa{\zeta}^{(j-1)}} denotes the updated global interference level from the \me{\ith{(j-1)}} information exchange of the local interference vector \me{\mbfa{\zeta}^{\set{b}(j-1)}, \forall b \in \mc{B}}.

Now, the local problem \eqref{eqn-dual-3} at each \ac{BS} \me{b} is solved either by the \ac{SCA} approach discussed in Section \ref{sec-3.2.1} or by using the \ac{MSE} reformulation approach outlined in Section \ref{sec-3.3}. Once the local problems are solved at each \ac{BS}, the new update for the global interference vector \me{\mbfa{\zeta}^{(j)}} and the dual variables \me{\mbfa{\nu}^{\set{b}(j)}} are performed at each \ac{BS} independently by exchanging the corresponding local copies of the interference vector \me{\mbfa{\zeta}^{\set{b}(j)}, \forall b \in \mc{B}}. Since the entries in \me{\mbfa{\zeta}^{(j)}} relate exactly to two \acp{BS} only, each entry in \me{\mbfa{\zeta}^{(j)}} can be updated by exchanging the local copies from the corresponding two \acp{BS}. For instance, the entry \me{\zeta^{(j)}_{l,\mc{U}_{b_k}(1),n,b}} depends on the local interference value \me{\zeta^{\set{b_k}(j)}_{l,\mc{U}_{b_k}(1),n,b}} assumed by the \ac{BS} \me{b_k} and the actual interference caused by \ac{BS} \me{b} as in \me{\zeta^{\set{b}(j)}_{l,\mc{U}_{b_k}(1),n,b}} as
\begin{equation}
\zeta_{l,\mc{U}_{b_k}(1),n,b}^{(j)} = \frac{1}{2} \, \left ( \, \zeta^{\set{b}(j)}_{l,\mc{U}_{b_k}(1),n,b} + \zeta^{\set{b_k}(j)}_{l,\mc{U}_{b_k}(1),n,b} \, \right ).
\label{zeta_update}
\end{equation}
The dual variable vector \me{\mbfa{\nu}^{\set{b_k}}}, which includes the stacked dual variables of the interference equality constraint at \ac{BS} \me{b_k}, are updated using the subgradient as
\begin{equation}\label{dual-sg-update}
\nu^{\set{b_k}(j)}_{l,k,n,b} = \nu^{\set{b_k}(j-1)}_{l,k,n,b} + \rho \, \left (\zeta^{\set{b_k}(j)}_{l,k,n,b} - \zeta^{(j)}_{l,k,n,b} \right ).
\end{equation}
The distributed precoder design using \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
{\allowdisplaybreaks 
\begin{algorithm}
\SetAlgoLined
\DontPrintSemicolon
\BlankLine
\SetKwInput{KwInit}{Initialize}
\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
\KwInit{\me{i=0} and the transmit precoders \me{{\mbf{m}}_{l,k,n}} randomly satisfying total power constraint \eqref{eqn-4.3}}
update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} \;
initialize the global interference vectors \me{\mbfa{\zeta}^{(0)} = \mbfa{0}^{\mathrm{T}}} \;
initialize the interference threshold \me{\mbfa{\nu}^{\set{b}(0)} \forall b \in \mc{B} = 0} \;
\ForEach{\ac{BS} \me{b \in \mc{B}}}{
	\Repeat{convergence or \me{i \geq I_{\max}}}{
		initialize \me{j=0} \;
		\Repeat{convergence or \me{j \geq J_{\max}}}{
			solve for \me{\mvec{m}{l,k,n}} and the local interference \me{\mbfa{\zeta}^{\set{b}}} using \eqref{eqn-dual-3} \;
			exchange \me{\mbfa{\zeta}^{\set{b}(j)}} among \acp{BS} in \me{\mc{B}} \;
			update dual variables in \me{\mbfa{\nu}^{\set{b}(j+1)}} using \eqref{dual-sg-update}\;
			update the consensus vector \me{\mbfa{\zeta}^{(j+1)}} using \eqref{zeta_update}\;
			\me{j = j + 1}\;
		}
		downlink precoded pilot transmission with \me{\mvec{m}{k,n}}\;
		update \me{\mvec{l}{k,n}} and notify to all \acp{BS} in \me{\mc{B}} using uplink precoded pilots as in \cite{komulainen2013effective}\;
		update \me{{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} approach \;
		$i = i + 1$ \;
	}
}
\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
\label{algo-3}
\end{algorithm}}
